A systematic search for transiting planets in the \KT\ data

### 2015-02-14 ms.tex
more results words

\newcommand{\paper}{\textsl{Article}}

@@

To limit memory consumption, in the periodic search, we actually profile (or
maximize) over \phase\ and \duration\ subject to the constraint that
$\TIC_\mathrm{const} > \TIC_\mathrm{var}$.
This results in a one-dimensional ``periodogram'' measuring the quality of
the fit as a function of period.
To choose the ``best'' candidate signal, we found that the best quantity to
select on was the signal-to-noise with which the depth was measured at a
given period, $\depth/\sigma_\depth$, computed using
Equations~(\ref{eq:periodic-depth}) and (\ref{eq:periodic-depth-uncert}).
Figure SOMEFIGURE shows the signal-to-noise of the depth measurement as a
function of period for SOMECANDIDATE.

@@

SOMEFIGURE shows the distribution of radius ratios and periods of candidates
from our sample.

>>>>

\newcommand{\paper}{\textsl{Article}}
\newcommand{\papertwo}{\textsl{Paper II}}

@@

To limit memory consumption, in the periodic search, we actually profile (or
maximize) over \phase\ and \duration\ subject to the constraint that
$\TIC_\mathrm{const} > \TIC_\mathrm{var}$ and requiring that the signal have
at least two observed transits.
This results in a one-dimensional ``periodogram'' measuring the quality of
the fit as a function of period.
To choose the ``best'' candidate signal, we found that the best quantity to
select on was the signal-to-noise with which the depth was measured at a
given period, $\depth/\sigma_\depth$, computed using
Equations~(\ref{eq:periodic-depth}) and (\ref{eq:periodic-depth-uncert}).
Figure SOMEFIGURE shows the signal-to-noise of the depth measurement as a
function of period for SOMECANDIDATE.

@@

SOMEFIGURE shows the observed distribution of planet candidates in our
catalog.
Using this and the detection efficiency function computed in the previous
section, we compute the occurrence rate as a function of period by ignoring
the measurement uncertainties and following the method described in the
Appendix of \citet{dfm}.
This function is shown in SOMEFIGURE and IS THIS CONSISTENT INTERESTING ETC?

In \papertwo, we will characterize the stars for each of our candidates in
detail but for now it's worth noting that about half (IS THIS TRUE) of our
planet candidates are orbiting M-type stars.
If this rate remains robust after stellar characterization and if these
numbers are representative of the \KT\ yields in upcoming Campaigns, this
will substantially increase the number of planets known to transit cool stars!
